Benchmarking FDR Methods - Summarizing Simulation Results

### 2017-11-03 datasets/simulations/analysis-03-plot-tsim-summaries.Rmd
Move t-test sim summary parsing from 01 to 03

>>>>

```{r, process-data, message=FALSE}
## list of results from 100 replication experiments
dl <- list.dirs("data-tsim/M100", recursive=FALSE, full.names=TRUE)

## parse each setting-block separately and save metrics in single file
for (dd in dl) {
    if (!file.exists(file.path(dd, "results-performanceMetrics-alpha05.rds"))) {
        fl <- list.files(dd, pattern=".rds", full.names=TRUE)
        tsbl <- list()
        for (f in fl) {
            ## read process data
            res <- readRDS(f)
            tsb <- plotsim_standardize(res, alpha = 0.05)
            tsbs <- tsb %>%
                filter(!(blabel %in% c("bl-df02", "bl-df04", "bl-df05", 
                                       paste0("ihw-a0", c(1:4, 6:9)), "ihw-a10")),
                       alpha == 0.05) %>%
                select(blabel, performanceMetric, value, rep)
            tsbl[[gsub(".*/(.*)\\.rds", "\\1", f)]] <- tsbs
        }
        tsbc <- as.tibble(bind_rows(tsbl, .id = "param"))
        saveRDS(tsbc, file.path(dd, "results-performanceMetrics-alpha05.rds"))
    }
}
```
